Initial Analysis

### 2019-05-29 Initial_Analysis.Rmd
Done first analysis. Next step fix Transboundary Index and include step 3 (if species has been catch at least once in that gridcell)

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel" # for parallelization
)

@@

@@

TenFifty <- Results_Data %>% 
  filter(Model_Index >= 50,
         Trans_Index >= 0.10) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(n_Trans_Spp = n()) %>% 
  filter(Model_Index == 50)
  head(Results_Data)

@@

World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))

head(World_EEZs)

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 3832) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 10000) %>% 
  left_join(TenFifty, by ="Name") %>% 
  filter(!is.na(n_Trans_Spp)) %>% 
  st_transform(crs = 4326)

head(World_EEZs_simple)

ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_Trans_Spp))

>>>>

#### Library ####
packages <- c(
  "readxl", # Read dataframe
  "data.table", # Read dataframe (Fast!)
  "dplyr", # Data manipulation
  "tidyr", # Data manipulation
  "ggplot2", #Nice grpahs and spatial analysis
  "wesanderson",
  # "cowplot",
  # "rgdal",
  # "RColorBrewer",
  # "knitr",
  # "kableExtra",
  # "ggrepel",
  # "gridExtra",
  # "ggmap",
  # "rgeos",
  # "stringr",
  # "stringer",
  "spdep", # for poly2nb
  "sf", #Spatial analysis 
  "sp", #Spatial analysis 
  "purrr",#Spatial analysis
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  # "png", # For reading plots in chunk codes
  # "grid" # For reading plots in chunk codes
  "parallel" # for parallelization
)

@@

ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(6,"line")
  )
}

@@

TenFifty <- Results_Data %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  group_by(Name,Model_Index) %>% 
  summarise(n_Trans_Spp = n()) %>% 
  filter(Model_Index == 100)
  # head(Results_Data)

@@

# The path
path_world <- paste(Data_Path,"Spatial_Data/SAU_Shapefile",sep="")
# #The File
fnam_world <- "SAUEEZ_July2015.shp"
# #Load it!
# 
World_EEZs <- st_read(dsn = path_world,
                      layer =file_path_sans_ext(fnam_world))
# 
# head(World_EEZs)

World_EEZs_simple <- World_EEZs %>% 
  st_transform(crs = 4326) %>% # 4326
  st_simplify(preserveTopology = TRUE, dTolerance = 1) %>%
  left_join(TenFifty, by ="Name") %>%
  filter(!is.na(n_Trans_Spp)) #%>%
  # st_transform(crs = 3832)

# head(World_EEZs_simple)

pal <- wes_palette("Zissou1", 100, type = "continuous")

Plot <- ggplot(World_EEZs_simple) +
  geom_sf(aes(fill = n_Trans_Spp)) +
  scale_fill_gradientn(colours = pal) +
  ggtheme_map()

ggsave("MI_100_TI_all_plot.png",
       plot = Plot,
       width = 16,
       height = 8,
       units = "in",
       path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

### Map exploration

# Salvador <- Results_Data %>% 
#   filter(Name == "El Salvador",
#          Model_Index >= 50)
# 
# Guat_Pac <- Results_Data %>% 
#   filter(Name == "Guatemala (Pacific)",
#          Model_Index >= 50)

Spp_Results <- Results_Data %>% 
  filter(Model_Index >= 50#,
         # Trans_Index >= 0.10
         ) %>% 
  group_by(TaxonKey,Model_Index) %>% 
  summarise(n_Trans_Spp = n()/2)

ggplot(Spp_Results) +
  geom_bar(
    aes(
      x = as.character(TaxonKey),
      y = n_Trans_Spp
    ),
    stat = "identity"
  ) +
  facet_wrap(~Model_Index,
             scales = "free")
